---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(displease)
```

# displease

<!-- badges: start -->
![](https://img.shields.io/badge/cool-useless-green.svg)
<!-- badges: end -->

The `displease` package provides non-linear interpolation between numeric values.  

It is a replacement for `seq()` for when you want a sequence between two values which is **not** equally spaced.

Easing can look much better than strict linear interpolation when applied  to 
objects moving spatially.

`displease` = **displ** + **ease**. The results are often used for 
animating visual **displacement**, and the non-linear interpolation is 
performed by applying an **easing** function.


## Installation

You can install from [GitHub](https://github.com/coolbutuseless/displease) with:

``` r
# install.package('remotes')
remotes::install_github('coolbutuseless/displease)
```

## What's in the box?

* `seq_ease(x1, x2, n, type)` - create a sequence of length `n`
   between `x1` and `x2`. Apply the easing function given by `type`.
* type is one of: `sine-in`, `sine-out`, `sine-in-out`, `quad-in`, `quad-out`, `quad-in-out`, `cubic-in`, `cubic-out`, `cubic-in-out`, `quart-in`, `quart-out`, `quart-in-out`, `quint-in`, `quint-out`, `quint-in-out`, `exp-in`, `exp-out`, `exp-in-out`, `circle-in`, `circle-out`, `circle-in-out`, `back-in`, `back-out`, `back-in-out`, `elastic-in`, `elastic-out`, `elastic-in-out`

The following graph shows the `seq_ease()` output for `n = 100` for
all the different easing functions with given extens of `x1 = 0` and `x2 = 1`

   
```{r echo=FALSE, fig.height = 10}
suppressPackageStartupMessages({
library(dplyr)
library(ggplot2)
library(purrr)
})


names   <- c('sine', 'quad', 'cubic', 'quart', 'quint', 'exp', 'circle', 'back', 'elastic')
methods <- c('in', 'out', 'in-out')

df <- as_tibble(expand.grid(method = methods, name = names)) %>%
  mutate(
    type   = paste(name, method, sep="-")
  )

ys <- map_dfr(df$type, ~tibble(type = .x, x = 1:100, y = seq_ease(type = .x)))

df <- left_join(df, ys, by = 'type')


ggplot(df) + 
  geom_line(aes(x, y)) + 
  facet_grid(name ~ method) + 
  theme_bw() + 
  scale_y_continuous(name = NULL, breaks = c(0, 1)) + 
  scale_x_continuous(name = NULL, breaks = c(0, 100)) +
  theme(axis.title = element_blank(), axis.text.x = element_blank()) + 
  coord_fixed(50)

```



## Example


```{r example}
library(displease)

# normal linear interpolation using seq()
(y_linear       <- seq(1, 10, length.out = 10))

# Non-linear interpolation using {displease}
(y_cubic_in     <- seq_ease(1, 10, n=10, type = 'cubic-in'))
(y_cubic_in_out <- seq_ease(1, 10, n=10, type = 'cubic-in-out'))

plot(1:10, y_linear      , type = 'b')
plot(1:10, y_cubic_in    , type = 'b')
plot(1:10, y_cubic_in_out, type = 'b')
```


## Related Software

* [tweenr](https://github.com/thomasp85/tweenr) is a more general purpose package 
  which will interpolate other types besides numeric values e.g. dates and colours.
  Expected data input is data.frames, or lists of data.frames. See for example
  `tweenr::tween_numeric()`
  

## Acknowledgements

* R Core for developing and maintaining such a wonderful language.
* CRAN maintainers, for patiently shepherding packages onto CRAN and maintaining
  the repository
